Towards End-user Web Scraping For Customization

### 2021-02-14 paper.tex
fix reference dates

This type of divide between tasks appears in other domains. In data
science, workflows revolve between cleaning and using data but this
often happens in different environments. The creators of Wrex
\citep{drosos2020}, an end-user programming-by-example system for data
wrangling, reported that ``although data scientists were aware of and
appreciated the productivity benefits of existing data wrangling tools,
having to leave their native notebook environment to perform wrangling
limited the usefulness of these tools.'' This was a major reason Wrex
was developed as an add-on to Jupyter notebooks, the environment in
which data scientists use their data. In web scraping, if a user comes
across an omission while working with data scraped from a website, they
need to switch from the environment in which they are using the data to
the environment in which they created their scraping code in order to
edit and re-run it. This can be seen in many end-user web scraping
systems like Rousillon \citep{chasins2018} and commercial tools like
import.io \citep{zotero-77}, dexi.io \citep{dexi.io}, Octoparse
\citep{zotero-83} and ParseHub \citep{zotero-86}. In web customization,
the creators of Vegemite \citep{lin2009}, a system for end-user
programming of mashups, reported that participants of its user study
thought ``it was confusing to use one technique to create the initial
table, and another technique to add information to a new column.'' This
hints at the need for both a unified environment and a unified workflow.

>>>>

This type of divide between tasks appears in other domains. In data
science, workflows revolve between cleaning and using data but this
often happens in different environments. The creators of Wrex
\citep{drosos2020}, an end-user programming-by-example system for data
wrangling, reported that ``although data scientists were aware of and
appreciated the productivity benefits of existing data wrangling tools,
having to leave their native notebook environment to perform wrangling
limited the usefulness of these tools.'' This was a major reason Wrex
was developed as an add-on to Jupyter notebooks, the environment in
which data scientists use their data. In web scraping, if a user comes
across an omission while working with data scraped from a website, they
need to switch from the environment in which they are using the data to
the environment in which they created their scraping code in order to
edit and re-run it. This can be seen in many end-user web scraping
systems like Rousillon \citep{chasins2018} and commercial tools like
import.io \citep{import.io}, dexi.io \citep{dexi.io}, Octoparse
\citep{octoparse} and ParseHub \citep{parsehub}. In web customization,
the creators of Vegemite \citep{lin2009}, a system for end-user
programming of mashups, reported that participants of its user study
thought ``it was confusing to use one technique to create the initial
table, and another technique to add information to a new column.'' This
hints at the need for both a unified environment and a unified workflow.
